Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-09-04 paper/tex/analysis.tex
fixed minor grammar errors, added affiliation

The goal of this study is to evaluate the degree to which \pzpdf s of each method can be trusted for a generic analysis.
The overloaded ``$p(z)$'' is a widespread abuse of notation that obfuscates this goal, so we will dedicate some attention to breaking it apart.
Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature.
As a result, each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$ as well as a true likelihood $p(d \vert z_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ is in general not accessible unless the photometry is in fact drawn from the true \pz\ likelihoods, a mock catalogue generation procedure that has not yet appeared in the literature and was not performed for this work.

@@

A quantile of a distribution is the value $q$ at which the CDF of the distribution is equal to $Q$; percentiles and quartiles are familiar examples of linearly spaced sets of 100 and 4 quantiles, respectively.
The quantile-quantile (QQ) plot serves as a graphical visualization for comparing two distributions, where the quantiles of one distribution are plotted against the quantiles of the other distribution, providing an easy way to qualitatively assess the consistency between an estimated distribution and a true distribution.
The closer the QQ plot is to diagonal, the closer the match between the distributions.
% In this paper, QQ plots are used for two purposes: (1) for comparing $N(z)$ from \pzpdf s (estimated using Eq.~\ref{eq:stacked}) with the true $N(z)$, and (2) for assessing the overall consistency of an ensemble of \pzpdf s with their true redshifts on a population level, where the distribution of the PIT values (see previous section) is compared to a uniform distribution between $0$ and $1$.
%\red{is this enough reason to include both?--SJS}
%\aim{Maybe we should explain why we expect the distribution of CDFs to be uniform.}\red{Note: this is just describing the PIT.  I'm going to swap the order of PIT to come before this, and then say we are evaluating the distribution of PIT values.  I will also add why we expect this to be uniform--SJS}

>>>>

The goal of this study is to evaluate the degree to which \pzpdf s of each method can be trusted for a generic analysis.
The overloaded ``$p(z)$'' is a widespread abuse of notation that obfuscates this goal, so we dedicate attention to dismantling it here.
Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature.
As a result, each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$ as well as a true likelihood $p(d \vert z_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ is in general not accessible unless the photometry is in fact drawn from a ground truth for the joint probability density of redshift and photometry $p(z, d)$.
In contrast, existing mock catalogs produce redshift-photometry pairs $(z, d)$ by a deterministic algorithm that does not correspond to a joint probability density from which one can take samples.
In these cases there is no ``true PDF'' for an individual object, and most measures of PDF fidelity will necessarily be restricted to probing the quality of the ensemble of \pzpdf s.
(See \S,\ref{sec:futureexperiments} for a discussion of how one might circumvent this limitation.)

@@

A quantile of a distribution is the value $q$ at which the CDF of the distribution is equal to $Q$; percentiles and quartiles are familiar examples of linearly spaced sets of 100 and 4 quantiles, respectively.
The quantile-quantile (QQ) plot serves as a graphical visualization for comparing two distributions, where the quantiles of one distribution are plotted against the quantiles of the other distribution, providing an intuitive way to qualitatively assess the consistency between an estimated distribution and a true distribution.
The closer the QQ plot is to diagonal, the closer the match between the distributions.
% In this paper, QQ plots are used for two purposes: (1) for comparing $N(z)$ from \pzpdf s (estimated using Eq.~\ref{eq:stacked}) with the true $N(z)$, and (2) for assessing the overall consistency of an ensemble of \pzpdf s with their true redshifts on a population level, where the distribution of the PIT values (see previous section) is compared to a uniform distribution between $0$ and $1$.
%\red{is this enough reason to include both?--SJS}
%\aim{Maybe we should explain why we expect the distribution of CDFs to be uniform.}\red{Note: this is just describing the PIT.  I'm going to swap the order of PIT to come before this, and then say we are evaluating the distribution of PIT values.  I will also add why we expect this to be uniform--SJS}

### 2019-09-04 paper/tex/appendix.tex
fixed minor grammar errors, added affiliation

\annz, \gpz, and \metaphor\ show possible signs of overtraining: showing exaggerated peaks and troughs relative to the training set.  Further investigation on overtraining is needed, if present this is an obstacle that may be overcome with adjustment of the implementation.

@@

Figure~\ref{fig:nz_stats} shows the quantitative Kolmogorov-Smirnoff (KS), Cramer-Von Mises (CvM), and Anderson Darling (AD) test statistics for each of the codes for the $\hat{N}(z)$ based measures.  The horizontal lines show the the result of a bootstrap resampling of the training set using 30,000 samples for \trainz.  As mentioned in Section~\ref{sec:pitqq} this represents a conservative idealized limit on expected performance for a modest-sized representative training set of galaxies.  The AD bootstrap statistic is elevated due to this statistic's sensitivity to distribution tails.
The stacked estimators of the redshift distribution for \cmnn\ and \trainz\ best estimate $\tilde{N}(z)$ under these metrics, and \bpz, \gpz, and \tpz\ are within a factor of two of the conservative limit for all statistics.  The only codes that do especially poorly are \eazy, \lephare, \metaphor, and \skynet.
It is unsurprising that \cmnn\ scores well, as with a nearly complete and representative training set choosing neighbouring points in color/magnitude space to construct an estimator should lead to excellent agreement in the final $\hat{N}(z)$.

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withbootstrap.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.  Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ actually outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.  \skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

>>>>

\annz, \gpz, and \metaphor\ feature exaggerated peaks and troughs relative to the training set, a potential sign of overtraining.
Further investigation on overtraining is needed, if present this is an obstacle that may be overcome with adjustment of the implementation.

@@

Figure~\ref{fig:nz_stats} shows the quantitative Kolmogorov-Smirnoff (KS), Cramer-Von Mises (CvM), and Anderson Darling (AD) test statistics for each of the codes for the $\hat{N}(z)$ based measures.
The horizontal lines show the the result of a bootstrap resampling of the training set using 30,000 samples for \trainz, representing a conservative idealized limit on expected performance for a modest-sized representative training set of galaxies, as mentioned in Section~\ref{sec:pitqq}.
The AD bootstrap statistic is elevated due to its sensitivity to the tails of distributions.
The stacked estimators of the redshift distribution for \cmnn\ and \trainz\ best estimate $\tilde{N}(z)$ under these metrics, whereas \eazy, \lephare, \metaphor, and \skynet\ underperform; \bpz, \gpz, and \tpz\ are within a factor of two of the conservative limit for all statistics.
It is unsurprising that \cmnn\ scores well, as with a nearly complete and representative training set choosing neighbouring points in color/magnitude space to construct an estimator should lead to excellent agreement in the final $\hat{N}(z)$.

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withbootstrap.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

### 2019-09-04 paper/tex/discussion.tex
fixed minor grammar errors, added affiliation

Furthermore, our metrics are not necessarily able to assess the fidelity of individual \pzpdf s relative to true posteriors.
Metric-specific performance implies that we may need multiple \pzpdf\ approaches tuned to each metric in order to maximize returns over all science cases in large upcoming surveys.

@@

This initial paper explored code performance in idealized conditions with perfect catalog-based photometry and representative training data.
A top priority for a follow-up study is to test realistic forms of incomplete, erroneous, and non-representative template libraries and training sets as well as the impact of other forms of external priors that must be ingested by the codes, major concerns in \citet{Newman:2015, Masters:2017}.
We plan to perform a full sensitivity analysis on a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which potential training set galaxies are most likely to be excluded.
In addition to outright redshift failures we will model the inclusion of a small number of high-confidence yet false redshifts due to emission line misidentification or noise spikes.

@@

>>>>

Furthermore, our metrics are not necessarily able to assess the fidelity of individual \pzpdf s relative to true posteriors: in the absence of a ``true PDF'' from which redshifts are drawn, it is difficult to construct metrics to measure performance for individual galaxies rather than ensembles.
(The CDE Loss metric of section~\ref{sec:CDE_loss} is an exception to this rule.)
A lack of appropriate metrics more sophisticated than the CDE Loss remains an open issue for science cases requiring accurate individual galaxy PDFs.
The metric-specific performance demonstrated in this paper implies that we may need multiple \pzpdf\ approaches tuned to each metric in order to maximize returns over all science cases in large upcoming surveys.

@@

This initial paper explored code performance in idealized conditions with perfect catalog-based photometry and representative training data.
A top priority for a follow-up study is to test realistic forms of incomplete, erroneous, and non-representative template libraries and training sets as well as the impact of other forms of external priors that must be ingested by the codes, major concerns in \citet{Newman:2015, Masters:2017}.
Outright redshift failures due to emission line misidentification or noise spikes may be modeled by the inclusion of a small number of high-confidence yet false redshifts.
We plan to perform a full sensitivity analysis on a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which potential training set galaxies are most likely to be excluded.

@@

Section~\ref{sec:metrics} discussed the difficulty in evaluating PDF accuracy for individual objects.
In a follow-up study, we will
 % use generative adversarial networks\citep[(GANs)][]{Goodfellow:14} trained on the simulation data to
generate ``true PDF'' distributions, yielding a dataset that enables a test of PDF accuracy for individual galaxies rather than solely ensembles.

### 2019-09-04 paper/tex/introduction.tex
fixed minor grammar errors, added affiliation

Though the standard has long been for each galaxy in a photometric catalogue to have a \pz\ point estimate and Gaussian error bar; however, as use in precision cosmology measurements became more prevalent there was a realization that point-estimate photo-$z$'s were inadequte \citep{mandelbaum:2008}.  The nontrivial mapping between broad band fluxes and redshift renders a simplistic point estimate inadequate to quantify the uncertainty landscape by neglecting degenerate redshift solutions.
Far from a hypothetical situation, this degeneracy is a real consequence of the same deep imaging that enables larger galaxy catalogue sizes.
The lower luminosity and higher redshift populations captured by deeper imaging introduce major physical systematics to \pz s, among them the Lyman break/Balmer break degeneracy, that did not affect shallower large area surveys like the Sloan Digital Sky Survey \citep[\textsc{SDSS},][]{York:00} and Two Micron All Sky Survey \citep[\textsc{2MASS},][]{Skrutskie:06}.

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases, (e.~g.~\citet{Erben:2013}, \citet{de_Jong:17}), provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

There are numerous techniques for deriving \pzpdf s, yet no one method has been established as clearly superior.  In fact, in the absence of simulated data drawn from known redshift distributions, the very concept of a ``true PDF'' for an individual galaxy is somewhat ill-defined, and we must instead rely on measures of ensemble behaviour to characterize PDF quality (see \S\,\ref{sec:metrics} for further discussion).  This caveat aside, quantitative comparisons of \pz\ methods have been made before; the \Pz\ Accuracy And Testing \citep[\textsc{PHAT},][]{Hildebrandt:10} effort focused on \pz\ point estimates derived from many photometric bands.
\citet{Rau:2015} introduced a new method for improving \pzpdf s using an ordinal classification algorithm.
\textsc{DES} compared several codes for \pz\ point estimates and a subset with \pzpdf\ information \citep{Sanchez:14} and examined summary statistics of \pzpdf s for tomographically binned galaxy subsamples \citep{Bonnett:16}.

This paper is distinguished by its focus on the evaluation criteria for \pzpdf s and interpretation thereof. This is a key project of the Photometric Redshifts working group of the \lsstdesc\ that aims to perform a comprehensive sensitivity analysis of \pzpdf\ techniques in order to ultimately select those that will become part of the \lsst\ pipelines.  These plans are laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.

>>>>

Though the standard has long been for each galaxy in a photometric catalogue to have a \pz\ point estimate and Gaussian error bar, even early applications of \pz s in precision cosmology indicate the inadequacy of point estimates \citep{mandelbaum:2008} to encapsulate the degeneracies resulting from the nontrivial mapping between broad band fluxes and redshift.
Far from a hypothetical situation, this degeneracy is a real consequence of the same deep imaging that enables larger galaxy catalogue sizes.
The lower luminosity and higher redshift populations captured by deeper imaging introduce major physical systematics to \pz s, among them the Lyman break/Balmer break degeneracy, that did not affect shallower large area surveys like the Sloan Digital Sky Survey \citep[\textsc{SDSS},][]{York:00} and Two Micron All Sky Survey \citep[\textsc{2MASS},][]{Skrutskie:06}.

To fully characterize such physical degeneracies, later photometric galaxy catalogue data releases, (e.~g.~\citet{Erben:2013}, \citet{de_Jong:17}), provide a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

There are numerous techniques for deriving \pzpdf s, yet no one method has been established as clearly superior.
In fact, in the absence of simulated data drawn from known redshift distributions, the very concept of a ``true PDF'' for an individual galaxy is unavailable, and we must instead rely on measures of ensemble behaviour to characterize PDF quality (see \S\,\ref{sec:metrics} for further discussion).
This caveat aside, quantitative comparisons of \pz\ methods have been made before; the \Pz\ Accuracy And Testing \citep[\textsc{PHAT},][]{Hildebrandt:10} effort focused on \pz\ point estimates derived from many photometric bands.
\citet{Rau:2015} introduced a new method for improving \pzpdf s using an ordinal classification algorithm.
\textsc{DES} compared several codes for \pz\ point estimates and a subset with \pzpdf\ information \citep{Sanchez:14} and examined summary statistics of \pzpdf s for tomographically binned galaxy subsamples \citep{Bonnett:16}.

This paper is distinguished from other comparisons of \pz\ methods by its focus on the evaluation criteria for \pzpdf s and interpretation thereof.
We aim to perform a comprehensive sensitivity analysis of \pzpdf\ techniques in order to ultimately select those that will become part of the \lsst\ pipelines, as part of a key project of the Photometric Redshifts working group of the \lsstdesc, described in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.

### 2019-09-04 paper/tex/methods.tex
fixed minor grammar errors, added affiliation

Here we summarize the twelve \pzpdf\ codes compared in this study, summarized in Table~\ref{tab:list_of_codes}, which include both established and emerging approaches in template fitting and machine learning.
Though not exhaustive, this sample represents codes for which there was sufficient expertise within the \lsstdesc\ Photometric Redshifts Working Group.  Some aspects of data treatment were left to the individual code runners, for example, whether/how to split the available data with known redshifts into separate training and validation sets. Another key difference is the treatment of non-detections in one or more bands: some codes choose to ignore a band, others replace the value with either an estimate for the detection limit, the mean of other values in the training set, or another default value. There are varying conventions among machine learning based codes for treatment of non-detections, and no one prescription dominates in the photo-z literature. The specific choices for each code affect the results, and contribute to the implicit prior influencing their output. However, we remind the reader that only 2.0 per cent of our sample has non-detections, almost exclusively in the u-band, and thus should not dominate the code performance differences.  The authors welcome interest from those outside \lsstdesc\ to have their codes assessed in future investigations that build upon this one.

@@

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a \chisq\ merit function using the observed and model fluxes:
\begin{equation} \label{eq_temp_chi}
\chi^2(z,T,A) = \sum_i^{N_{\rm filt}}\left(\frac{F^i_{\rm{obs}} - A \, F^i_{\rm{pred}}(T,z)}{\sigma^i_{\rm{obs}}}\right)^2
\end{equation}
\noindent  where $A$ is a normalization factor, $F^i_{\rm{pred}}(T,z)$ is the flux predicted for a template $T$ at redshift $z$. $F^i_{\rm{obs}}$ is the observed flux in a given band $i$ and $\sigma^i_{\rm{obs}}$ is the observed flux error. $N_{\rm filt}$ is the total number of filters, in our case the six $ugrizy$ LSST filters.  Specific implementation details of each code, e.~g.~prior form and implementation, are described below.

@@

Photometric Analysis for Redshift Estimate \citep[\lephare\footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}},][]{Arnouts:99,Ilbert:06} matches observed colors with those predicted from a template set, which can be semi-empirical or entirely synthetic, directly according to the $\chi^2$ form given in Equation~\ref{eq_temp_chi}.
In words, the likelihood is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which is the \lsst\ $ugrizy$ filters in this case.
The reported \pzpdf\ is an arbitrary normalization of the likelihood evaluated on the output redshift grid.
%\textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.

@@

Bayesian Photometric Redshift \citep[\bpz\footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}},][]{Benitez:00} determines the likelihood $p(C \vert z, T)$ of a galaxy's observed colours $C$ for a set of SED templates $T$ at redshifts $z$.
The \bpz\ likelihood is related to the \chisq\ likelihood by $p(C \vert z, T) \propto \exp[- \chi^{2} / 2]$.
Given a Bayesian prior $p(z, T \vert m_{0})$ over apparent magnitude $m_0$ and type $T$, and assuming that the SED templates are spanning and exclusive, \bpz\ constructs the redshift posterior $p(z \vert C, m_0)$ by marginalizing over all SED templates as in \citep[Eq.~3 from][]{Benitez:00}, corresponding to setting the parameter \texttt{PROBS\_LITE=TRUE} in the \bpz\ parameter file.
The \bpz\ prior is the product of an SED template proportion that varies with apparent magnitude $p(T \vert m_{0})$ and a prior $p(z \vert T, m_{0})$ over the expected redshift as a function of apparent magnitude and SED template.

Here we test \bpz-v 1.99.3 with the DC1 template set of Section~\ref{sec:buzztemplates}.
To keep the number of free parameters manageable, the DC1 template set is pre-sorted by the rest-frame $u-g$ colour and split into three broad classes of SED template, equivalent to the E, Sp and Im/SB types in .
The Bayesian prior term $p(T \vert m_{0})$ was derived directly from the DC1 training set, and the other term $p(z \vert T, m_{0})$ was chosen to be the best fit for the eleven free parameters of the functional form of \citet{Benitez:00}.  We use template interpolation, creating two linearly interpolated templates between each basis SED (sorted by rest-frame $u-g$ colour) by setting the parameter \texttt{INTERP=2}.
%For photo-$z$ point estimates we use the \texttt{Z\_B} output parameter.
Prior to running the code, the non-detection placeholder magnitude was replaced with an estimate of the one-$\sigma$ detection limit for the undetected band as a proxy for a value close to the estimated sky noise threshold.

@@

\annz \footnote{\url{https://github.com/IftachSadeh/ANNZ}} \citep{Sadeh:16} employs several machine learning algorithms, including artificial neural networks (ANN), boosted decision tree, and k-nearest neighbour (KNN) regression.
In addition to accounting for errors on the input photometry, \annz\ uses the KNN-uncertainty estimate of \citet{Oyaizu:08} to quantify uncertainty in the choice of method over multiple runs.
Using the Toolkit for Multivariate Data Analysis with ROOT\footnote{\url{http://tmva.sourceforge.net/}}, it can return the results of running a single machine learning algorithm, a ``best'' choice of the results from simultaneously running multiple algorithms, or a combination of the results of multiple algorithms weighted by their method uncertainties averaged over multiple runs.
%\textsc{ANNz2} is capable of producing both photo-$z$ point estimates and redshift posterior probability distributions $p(z)$.
% It can also perform classifications, and supports reweighting between samples.
% \annz\ propagates the intrinsic uncertainty on the input parameters and the uncertainty in the machine learning method to the expected photo-$z$ solution, averaged over multiple runs weighted based on the performance of each run.

@@

Here, we make two modifications to the implementation of \citet{Graham:17} to comply with the controlled experimental conditions.
First, we do not impose non-detections on galaxies fainter than the expected \lsst\ 10-year limiting magnitude or bright enough to saturate with \lsst's CCDs, instead using all of the photometry for the DC1 test and training sets.
Second, we apply the initial colour cut to the training set before calculating the Mahalanobis distance in order to accelerate processing and use a magnitude pseudo-prior as in \citet{Graham:17}, but for both we use cut-off values corresponding to the DC1 training set galaxies' colours and magnitudes.

@@

To smooth the long tail in the distribution of magnitude errors, we use the log of the magnitude errors, improving numerical stability and eliminating the need for constraints on the optimization process.
% We use principaphoto-\mathinhead{$z$}{z} interim posteriorsl component analysis (PCA) to decorrelate the data
% WHAT IS BEING DECORRELATED HERE?
Unobserved magnitudes $x_{\rm u} = \mu_{\rm u} + \Sigma_{\rm uo}\Sigma_{\rm oo}^{-1}(x_{\rm o} - \mu_{\rm o})$ were imputed from observed magnitudes $x_{\rm o}$ and the training set mean $\mu$ and covariance $\Sigma$ using a linear model.
This is the optimal expected value of the unobserved variables given the observed ones under the assumption that the distribution is jointly Gaussian; note that this reduces to a simple average if the covariates are independent with $\Sigma_{\rm uo} = 0$.
We reserved for validation 20\% of the training set and used the Variable Covariance option in \textsc{GPz} with 200 basis functions (see \citet{Almosallam:15b} for details), neglecting to apply cost-sensitive learning options.

>>>>

Here we summarize the twelve \pzpdf\ codes compared in this study, also in Table~\ref{tab:list_of_codes}, which include both established and emerging approaches in template fitting and machine learning.
Though not exhaustive, this sample represents codes for which there was sufficient expertise within the \lsstdesc\ Photometric Redshifts Working Group.
Some aspects of data treatment were left to the individual code runners, for example, whether/how to split the available data with known redshifts into separate training and validation sets.

Another key difference is the treatment of non-detections in one or more bands: some codes ignore incomplete bands, while others replace the value with either an estimate for the detection limit, the mean of other values in the training set, or another default value.
There are varying conventions among machine learning based codes for treatment of non-detections, and no one prescription dominates in the \pz\ literature.
The specific choices for each code affect the results and contribute to the implicit prior influencing their output.
However, we remind the reader that only 2.0 per cent of our sample has non-detections, almost exclusively in the $u$-band, and thus should not dominate the code performance differences.
The authors welcome interest from those outside \lsstdesc\ to have their codes assessed in future investigations that build upon this one.

@@

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a \chisq\ merit function using the observed and model fluxes:
\begin{equation} \label{eq_temp_chi}
\chi^2(z,T,A) = \sum_i^{N_{\rm filt}}\left(\frac{F^i_{\rm{obs}} - A \, F^i_{\rm{pred}}(T,z)}{\sigma^i_{\rm{obs}}}\right)^2
\end{equation}
\noindent where $A$ is a normalization factor, $F^i_{\rm{pred}}(T,z)$ is the flux predicted for a template $T$ at redshift $z$, $F^i_{\rm{obs}}$ is the observed flux in a given band $i$, $\sigma^i_{\rm{obs}}$ is the observed flux error, and $N_{\rm filt}$ is the total number of filters, in our case the six $ugrizy$ LSST filters.
In words, the likelihood is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which is the \lsst\ $ugrizy$ filters in this case.
Specific implementation details of each code, e.~g.~prior form and implementation, are described below.

@@

Photometric Analysis for Redshift Estimate \citep[\lephare\footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}},][]{Arnouts:99,Ilbert:06} uses the $\chi^2$ of Equation~\ref{eq_temp_chi} to match observed colors with those predicted from a template set, which can be semi-empirical or entirely synthetic, directly according to the
The reported \pzpdf\ is an arbitrary normalization of the likelihood evaluated on the output redshift grid.
%\textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.

@@

Bayesian Photometric Redshift \citep[\bpz\footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}},][]{Benitez:00} determines the likelihood $p(C \vert z, T)$ of a galaxy's observed colours $C$ for a set of SED templates $T$ at redshifts $z$.
The \bpz\ likelihood is related to the \chisq\ likelihood by $p(C \vert z, T) \propto \exp[- \chi^{2} / 2]$.
Given a Bayesian prior $p(z, T \vert m_{0})$ over apparent magnitude $m_0$ and type $T$, and assuming that the SED templates are spanning and exclusive, \bpz\ constructs the redshift posterior $p(z \vert C, m_0)$ by marginalizing over all SED templates with the form $p(z|C,m_0)\,\propto\, \sum_{T}p(C|z,T)\,p(z,T|m_0)$ \citep[Eq.~3 from][]{Benitez:00}, corresponding to setting the parameter \texttt{PROBS\_LITE=TRUE} in the \bpz\ parameter file.
The \bpz\ prior is the product of an SED template proportion that varies with apparent magnitude $p(T \vert m_{0})$ and a prior $p(z \vert T, m_{0})$ over the expected redshift as a function of apparent magnitude and SED template.

Here we test \bpz-v 1.99.3 with the DC1 template set of Section~\ref{sec:buzztemplates}.
To keep the number of free parameters manageable, the DC1 template set is pre-sorted by the rest-frame $u-g$ colour and split into three broad classes of SED template, equivalent to the E, Sp and Im/SB types.
The Bayesian prior term $p(T \vert m_{0})$ was derived directly from the DC1 training set, and the other term $p(z \vert T, m_{0})$ was chosen to be the best fit for the eleven free parameters of the functional form of \citet{Benitez:00}.
We use template interpolation, creating two linearly interpolated templates between each basis SED (sorted by rest-frame $u-g$ colour) by setting the parameter \texttt{INTERP=2}.
%For photo-$z$ point estimates we use the \texttt{Z\_B} output parameter.
Prior to running the code, the non-detection placeholder magnitude was replaced with an estimate of the one-$\sigma$ detection limit for the undetected band as a proxy for a value close to the estimated sky noise threshold.

@@

\annz \footnote{\url{https://github.com/IftachSadeh/ANNZ}} \citep{Sadeh:16} employs several machine learning algorithms, including artificial neural networks (ANN), boosted decision tree, and k-nearest neighbour (KNN) regression.
In addition to accounting for errors on the input photometry, \annz\ uses the KNN-uncertainty estimate of \citet{Oyaizu:08} to quantify uncertainty in the choice of method over multiple runs.
Using the Toolkit for Multivariate Data Analysis with ROOT\footnote{\url{http://tmva.sourceforge.net/}}, \annz\ can return the results of running a single machine learning algorithm, a ``best'' choice of the results from simultaneously running multiple algorithms (based on evaluation the cumulative distribution functions of validation set objects), or a combination of the results of multiple algorithms weighted by their method uncertainties averaged over multiple runs.
%\textsc{ANNz2} is capable of producing both photo-$z$ point estimates and redshift posterior probability distributions $p(z)$.
% It can also perform classifications, and supports reweighting between samples.
% \annz\ propagates the intrinsic uncertainty on the input parameters and the uncertainty in the machine learning method to the expected photo-$z$ solution, averaged over multiple runs weighted based on the performance of each run.

@@

Here, we make two modifications to the implementation of \citet{Graham:17} to comply with the controlled experimental conditions.
First, we do not impose non-detections on galaxies fainter than the expected \lsst\ 10-year limiting magnitude nor galaxies bright enough to saturate with \lsst's CCDs, instead using all of the photometry for the DC1 test and training sets.
Second, we apply the initial colour cut to the training set before calculating the Mahalanobis distance in order to accelerate processing and use a magnitude pseudo-prior as in \citet{Graham:17}, but for both we use cut-off values corresponding to the DC1 training set galaxies' colours and magnitudes.

@@

To smooth the long tail in the distribution of magnitude errors, we use the log of the magnitude errors, improving numerical stability and eliminating the need for constraints on the optimization process.
% We use principaphoto-\mathinhead{$z$}{z} interim posteriorsl component analysis (PCA) to decorrelate the data
% WHAT IS BEING DECORRELATED HERE?
Unobserved magnitudes $x_{\rm u} = \mu_{\rm u} + \Sigma_{\rm uo}\Sigma_{\rm oo}^{-1}(x_{\rm o} - \mu_{\rm o})$ were imputed from observed magnitudes $x_{\rm o}$ and the training set mean $\mu$ and covariance $\Sigma$ using a linear model.
This is the optimal expected value of the unobserved variables given the observed ones under the assumption that the distribution is jointly Gaussian; note that this reduces to a simple average if the covariates are independent with $\Sigma_{\rm uo} = 0$.
We reserved for validation 20\% of the training set and used the Variable Covariance option in \gpz\ with 200 basis functions (see \citet{Almosallam:15b} for details), neglecting to apply cost-sensitive learning options.
